---
title: "Weight of Fish"
author: "Kevin Brandon Salazar"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
## get data
```{r}
fishData=read.csv("Fish.csv")
```


## Perch
```{r}
perch = filter(fishData, Species == "Perch")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=perch,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variable for predicting weight are height and width so we used height and width to weight.

### Best Two regressor model

The best two predictor regressor model is height and width
```{r}
perchModel=lm(Weight~Height+Width, data=perch)
summary(perchModel)
```
For the best model for adjusted r squared is 0.94

## Pike
```{r}
pike = filter(fishData, Species == "Pike")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best two variable for predicting weight are length1 and length3 so we used length1 and length3 to predict weight.

### Best Two regressor model

The best two predictor regressor model is length1 and length3
```{r}
pikeModel=lm(Weight~Height+Width, data=pike)
summary(pikeModel)
```
For the best model for adjusted r squared is 0.86

## Roach

```{r}
roach = filter(fishData, Species == "Roach")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best two variable for predicting weight are length3 and width so we used length3 and width to predict weight.

### Best Two regressor model

The best two predictor regressor model is length3 and width
```{r}
roachModel=lm(Weight~Height+Width, data=roach)
summary(roachModel)
```
For the best model for adjusted r squared is 0.84

## Final Summary Statements
Among these model we found the best 